The impacts of demography on linked selection in maize

### 2015-07-01 manuscript.tex
significance

\documentclass{pnastwo}
\usepackage{cite}
\usepackage{color}
\usepackage{pgf}
%\usepackage{hyperref}
\usepackage[normalem]{ulem}
\newcommand{\jri}[1]{\textcolor{blue}{\emph{#1}} }

@@

\title{Demography and selection since maize domestication}
\author{Timothy M. Beissinger\affil{1}{Dept. of Plant Sciences, University of
    California, Davis, CA, USA}, Li Wang\affil{2}{Iowa State University, Ames, IA, USA}, Arun
  Durvasula\affil{1}{}, Kate Crosby\affil{1}{}, Matthew Hufford\affil{2}{}, \and Jeffrey
  Ross-Ibrarra\affil{1}{}\affil{3}{Genome Center and Center for population biology, University of
    California, Davis, CA, USA} }

\significancetext{This work is insignificant ;-)}

@@

\begin{abstract}
This is the abstract. It should probably be somewhere around 200 words.
\end{abstract}

>>>>

\documentclass{pnastwo}
\usepackage{cite}
\usepackage{color}
\usepackage{pgf}
%\usepackage{hyperref}
\usepackage[normalem]{ulem}
\newcommand{\jri}[1]{\textcolor{red}{\emph{#1}} }
\newcommand{\citex}{\textcolor{red}{\bf CITE}}
\newcommand{\X}{\textcolor{red}{\bf X}}

@@

\title{The impacts of demography on linked selection in maize}
\author{Timothy M. Beissinger\affil{1}{Dept. of Plant Sciences, University of
    California, Davis, CA, USA}, Li Wang\affil{2}{Iowa State University, Ames, IA, USA}, Arun
  Durvasula\affil{1}{}, Kate Crosby\affil{1}{}, Matthew Hufford\affil{2}{}, \and Jeffrey
  Ross-Ibrarra\affil{1}{}\affil{3}{Genome Center and Center for population biology, University of
    California, Davis, CA, USA} }

\significancetext{patterns of linked selection have been carefully evaluated in only a few species. how demography interacts with selection to impact genome-wide pattersn of diversity is still not well understood. also this work is significant (Beissinger b-test, p<0.01) }

@@

\begin{abstract}
This is the abstract. It should probably be longer than a tweet and shorter than 250 words.
\end{abstract}
